### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] sketch some of the semantics section

\subsection{$*$-autonomous and Duoidal Preorders}

@@

@@

@@

To construct suitable MAV Algebras, we use the preorder version of the
Chu construction \cite{barr}. The Chu construction builds
$*$-autonomous categories from symmetric monoidal closed categories
with pullbacks. In the preorder case, the requirement for preorders
simplifies to binary meets. Therefore, for this section, we let
$(A, \leq, \bullet, \epsilon, -\kern-9pt\bullet)$ be a symmetric
monoidal closed preorder with all binary meets.

>>>>

\subsection{$*$-autonomous and Duoidal Partial Orders}

\begin{definition}
  A \emph{partial order monoid (pomonoid)} $(\bullet, i)$ on a poset
  $(A, \leq)$ comprises a binary operator $\bullet : A \times A \to A$
  that is monotone in both arguments and an element $i \in A$ such
  that the usual monoid laws hold. A \emph{commutative pomonoid} is a
  pomonoid where additionally $x \bullet y = y \bullet x$.
\end{definition}

\begin{definition}
  A \emph{$*$-autonomous partial order} is ... TODO
\end{definition}

FIXME: cite that combinatorics book.
\begin{definition}
  Two pomonoids $(\bullet, i)$ and $(\rhd, j)$ on a partial order
  $(A, \leq)$ are in a \emph{duoidal} relationship if the following
  inequalities hold:
  \begin{enumerate}
  \item $(w \rhd x) \bullet (y \rhd z) \leq (w \bullet y) \rhd (x \bullet z)$
  \item $j \bullet j \leq j$
  \item $i \leq i \rhd i$
  \item $i \leq j$
  \end{enumerate}
\end{definition}

\begin{remark}
  In the case when the two pomonoids share a common unit (as in MAV),
  the last three conditions for a duoidal relationship are
  automatically satisfied.
\end{remark}

@@

\begin{definition}
  An \emph{MAV Algebra} is a structure $(A, \leq, ...)$
  \begin{enumerate}
  \item 
  \end{enumerate}
\end{definition}

\bob{Consequences of the definition, as listed in the Agda}

@@

\begin{theorem}
  The interpretation of SMAV proofs in an MAV Algebra is sound. \bob{elaborate...}
\end{theorem}

\subsection{MAV Frames}

\begin{definition}
  An \emph{MAV Frame} is a structure
  $(F, \leq, I, \parallel, \rhd, +)$ where $(F, \leq)$ is a partial
  order, $(F, \leq, I, \parallel)$ is a commutative pomonoid,
  $(F, \leq, I, \rhd)$ is a pomonoid, $+$ is a binary monotone
  function on $(F, \leq)$, and these structures satisfy the following:
  \begin{enumerate}
  \item $(w \rhd x) \parallel (y \rhd z) \leq (w \parallel y) \rhd (x \parallel z)$
  \item $(x + y) \parallel z \leq (x \parallel z) + (y \parallel z)$
  \item $(w \rhd x) + (y \rhd z) \leq (w + y) \rhd (x + z)$
  \item $I + I \leq I$
  \end{enumerate}
\end{definition}

\begin{remark}
  \bob{Connection to process algebras}
\end{remark}

\begin{proposition}
  \bob{The Cut-free system forms an MAV Frame}
\end{proposition}

@@

To construct suitable MAV Algebras, we use the poset version of the
Chu construction \cite{barr}. The Chu construction builds
$*$-autonomous categories from symmetric monoidal closed categories
with pullbacks. In the preorder case, the requirement for preorders
simplifies to binary meets. Therefore, for this section, we let
$(A, \leq, \bullet, \epsilon, -\kern-9pt\bullet)$ be a symmetric
monoidal closed preorder with all binary meets.
